### 2015-08-05 corral.tex
Removed vspace hacks for now.
Changed Figure into Fig.
Done with Sec 4

\whoop is a sound but imprecise static race analyzer. For developers who deem false alarms as unacceptable, we consider a method for leveraging the full or partial race-freedom guarantees provided by \whoop to accelerate \corral~\cite{lal2012corral}, a precise bug-finder used by Microsoft to analyze Windows drivers~\cite{lal2014powering}.  Because \corral operates on Boogie programs, it was easy to integrate it into our toolchain (see Figure~\ref{fig:whoop} -- C). Our technique, though, is general and capable in principle of accelerating any concurrency bug-finder that operates by interleaving threads at shared memory operations.

@@

\noindent\textbf{Race-Checking Instrumentation }
%
To detect data races with \corral, \whoop outputs a Boogie program instrumented with a simple, but effective encoding of race checks. Whenever there is a write access to a shared variable $s$, \whoop instruments the program as follows:
%
\begin{boogie}
s = e;         // original write
yield;         // allow for a context-switch
assert s == e; // check written value
\end{boogie}\vspace{-2mm}
%
Likewise, whenever there is a read access to $s$, \whoop instruments the program as follows:
%
\begin{boogie}
x = s;         // original read
yield;         // allow for a context-switch
assert x == s; // check read value
\end{boogie}\vspace{-2mm}
%
A \texttt{yield} statement denotes a nondeterministic context-switch, and is used by \corral to guide the sequentialization.

@@

Our partial-order reduction is able in principle to accelerate \corral for \emph{arbitrary} bug-finding in concurrent programs. Although we did preliminary explorations in this direction, identifying useful safety properties to check was challenging since there are typically no assertions in drivers. Thus, in the remainder of this paper, we only regard data races as bugs and use \corral solely to look for data races.

>>>>

\whoop is a sound but imprecise static race analyzer. For developers who deem false alarms as unacceptable, we consider a method for leveraging the full or partial race-freedom guarantees provided by \whoop to accelerate \corral~\cite{lal2012corral}, a precise bug-finder used by Microsoft to analyze Windows drivers~\cite{lal2014powering}.  Because \corral operates on Boogie programs, it was easy to integrate it into our toolchain (see Fig.~\ref{fig:whoop}--C). Our technique, though, is general and capable in principle of accelerating any concurrency bug-finder that operates by interleaving threads at shared memory operations.

@@

\noindent\textbf{Race-Checking Instrumentation }
%
To detect data races with \corral, \whoop outputs a Boogie program instrumented with a simple, but effective encoding of race checks. Whenever there is a write access to a shared variable $s$, \whoop instruments the program as follows:
%
\begin{boogie}
s = e;         // original write
yield;         // allow for a context-switch
assert s == e; // check written value
\end{boogie}%\vspace{-2mm}
%
Likewise, whenever there is a read access to $s$, \whoop instruments the program as follows:
%
\begin{boogie}
x = s;         // original read
yield;         // allow for a context-switch
assert x == s; // check read value
\end{boogie}%\vspace{-2mm}
%
A \texttt{yield} statement denotes a nondeterministic context-switch, and is used by \corral to guide the sequentialization.

@@

Our partial-order reduction is able in principle to accelerate \corral for \emph{arbitrary} bug-finding in concurrent programs. Although we did preliminary explorations in this direction, identifying useful safety properties to check was challenging since drivers typically contain no assertions. Thus, in this paper we use \corral solely to find data races.
